

%%% Choose a language %%%

\newif\ifEN
\ENtrue   % uncomment this for english
%\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
%\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
%\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Climbing route editor}
\def\ThesisAuthor{Tomáš Sláma}
\def\YearSubmitted{2022}

% department assigned to the thesis
\def\Department{Department of Applied Mathematics}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

\def\Supervisor{Martin Mareš}
\def\SupervisorsDepartment{Department of Applied Mathematics}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{IPP1}

\def\Dedication{%
I'm grateful for the support from my friends and family, namely Kateřina Sulková, Jakub Medek, Matěj Kripner, Jan Černý, Benjamin Schiller and Jakub Pelc.
I would also like to thank my supervisor Martin Mareš for patience and valuable feedback.
}

\def\AbstractEN{%
With the rising popularity of sport climbing and bouldering, there are increasing incentives to take it to the online space.
This thesis does so in way suitable for regular climbing gyms.
A workflow for creating 3D hold and wall models and the accompanying editor has been developed, so that routes can be copied from the real world to the virtual one and be interacted with using software in a more immersive way.
}

\def\AbstractCS{%
S rostoucí popularitou sportovního lezení a boulderingu roste i pobídka po přenesení sportu do online prostoru.
Tato práce tak činí způsobem přístupným pro běžná lezecká centra.
Byl vyvinut způsob tvorby 3D modelů chytů a stěn a doprovázející 3D editor, aby cesty z reálného světa mohly být přeneseny do toho virtuálního k interaktivnímu prohlížení pomocí softwaru.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{%
photogrammetry, routesetting, 3D modelling
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{\xxx{Thesis title in English}}
\def\DepartmentEN{\xxx{Name of the department in English}}
\def\DeptTypeEN{\xxx{Department}}
\def\SupervisorsDepartmentEN{\xxx{Superdepartment}}
\def\StudyProgrammeEN{\xxx{study programme}}
\def\StudyBranchEN{\xxx{study branch}}
\def\KeywordsEN{%
\xxx{{key} {words}}
}
\fi
